Code used to generate paper results : PMD analysis

### 2023-08-28 Paper_code-Database_CT.Rmd
Update with CTexploreR last version

```{r library, message = FALSE}
library(readxl)
library(readr)
library(CTexploreR)
library(Vennerable)
library(biomaRt)
library(tidyverse)
library(SummarizedExperiment)
library(UpSetR)
library(ComplexHeatmap)
library(circlize)
library(SingleCellExperiment)
library(org.Hs.eg.db)
library(clusterProfiler)
library(msigdbr)
library(DOSE)
library(BiocParallel)
library(patchwork)
library(Biostrings)
```

@@

```{r load_data, warning=FALSE, message=FALSE}
GTEX_data <- CTdata::GTEX_data()
normal_tissues_multimapping_data <- CTdata::normal_tissues_multimapping_data()
CCLE_data <- CTdata::CCLE_data()
TCGA_TPM <- CTdata::TCGA_TPM()
DAC_treated_cells_multimapping <- CTdata::DAC_treated_cells_multimapping()
load("../CTdata/eh_data/testis_sce.rda") 
load("../CTdata/eh_data/scRNAseq_HPA.rda")
load("../CTdata/eh_data/CT_mean_methylation_in_tissues.rda")
```

>>>>

```{r library, message = FALSE}
.libPaths("/storage/research/dduv/cbio-lg/rlib/Bioc318/", include.site = FALSE)
library(readxl)
library(readr)
library(CTexploreR)
library(Vennerable)
library(biomaRt)
library(tidyverse)
library(SummarizedExperiment)
library(UpSetR)
library(ComplexHeatmap)
library(circlize)
library(SingleCellExperiment)
library(org.Hs.eg.db)
library(clusterProfiler)
library(msigdbr)
library(DOSE)
library(BiocParallel)
library(patchwork)
library(Biostrings)
```

@@

```{r load_data, warning=FALSE, message=FALSE}
GTEX_data <- CTdata::GTEX_data()
normal_tissues_multimapping_data <- CTdata::normal_tissues_multimapping_data()
CCLE_data <- CTdata::CCLE_data()
TCGA_TPM <- CTdata::TCGA_TPM()
DAC_treated_cells_multimapping <- CTdata::DAC_treated_cells_multimapping()
testis_sce <- CTdata::testis_sce()
scRNAseq_HPA <- CTdata::scRNAseq_HPA()
CT_mean_methylation_in_tissues <- CTdata::CT_mean_methylation_in_tissues()
```

### 2023-08-28 Paper_code-PMD_analysis.Rmd
Update with CTexploreR last version

```{r library, message = FALSE}
library(readr)
library(CTexploreR)
library(biomaRt)
library(tidyverse)
library(SummarizedExperiment)
library(BiocParallel)
library(patchwork)
library(Biostrings)
```

@@

nonCT_per_gene_CD4_datasets <- bplapply(unique(nonCTmeth_inCD4$ensembl_gene_id),
                                      reorganize_data_ensembl, data = nonCTmeth_inCD4)
names(nonCT_per_gene_CD4_datasets) <- unique(nonCTmeth_inCD4$ensembl_gene_id)

p <- rep(NA, length(nonCT_per_gene_CD4_datasets))
for(i in 1:length(nonCT_per_gene_CD4_datasets)) {
 p[i] <- nrow(nonCT_per_gene_CD4_datasets[[i]]) > 1 &
   is.data.frame(nonCT_per_gene_CD4_datasets[[i]])
}
nonCT_per_gene_CD4_datasets <- nonCT_per_gene_CD4_datasets[p]

k <- rep(NA, length(nonCT_per_gene_CD4_datasets))
for(i in 1:length(nonCT_per_gene_CD4_datasets)) {
  k[i] <- nrow(nonCT_per_gene_CD4_datasets[[i]]) == 2
}

for (gene in names(nonCT_per_gene_CD4_datasets[k])) {
  tmp <- rep(NA, ncol(nonCT_per_gene_CD4_datasets[[gene]]))
  nonCT_per_gene_CD4_datasets[[gene]] <- rbind(nonCT_per_gene_CD4_datasets[[gene]], tmp)
  rownames(nonCT_per_gene_CD4_datasets[[gene]])[3] <-
    c("newborn","middle_age", "centenarian")[(!c("newborn","middle_age","centenarian") %in%
                                                rownames(nonCT_per_gene_CD4_datasets[[gene]]))]
  # naming the new row
}

for (gene in names(nonCT_per_gene_CD4_datasets)) {
  nonCT_per_gene_CD4_datasets[[gene]] <- arrange(nonCT_per_gene_CD4_datasets[[gene]],
                                              rownames(nonCT_per_gene_CD4_datasets[[gene]]))
  # Put rows in the right order
}

# load("data_rmd/nonCT_per_gene_CD4_datasets.rda")

>>>>

```{r library, message = FALSE}
.libPaths("/storage/research/dduv/cbio-lg/rlib/Bioc318/", include.site = FALSE)
library(readr)
library(CTexploreR)
library(biomaRt)
library(tidyverse)
library(SummarizedExperiment)
library(BiocParallel)
library(patchwork)
library(Biostrings)
```

@@

# nonCT_per_gene_CD4_datasets <- bplapply(unique(nonCTmeth_inCD4$ensembl_gene_id),
#                                       reorganize_data_ensembl, data = nonCTmeth_inCD4)
# names(nonCT_per_gene_CD4_datasets) <- unique(nonCTmeth_inCD4$ensembl_gene_id)
# 
# p <- rep(NA, length(nonCT_per_gene_CD4_datasets))
# for(i in 1:length(nonCT_per_gene_CD4_datasets)) {
#  p[i] <- nrow(nonCT_per_gene_CD4_datasets[[i]]) > 1 &
#    is.data.frame(nonCT_per_gene_CD4_datasets[[i]])
# }
# nonCT_per_gene_CD4_datasets <- nonCT_per_gene_CD4_datasets[p]
# 
# k <- rep(NA, length(nonCT_per_gene_CD4_datasets))
# for(i in 1:length(nonCT_per_gene_CD4_datasets)) {
#   k[i] <- nrow(nonCT_per_gene_CD4_datasets[[i]]) == 2
# }
# 
# for (gene in names(nonCT_per_gene_CD4_datasets[k])) {
#   tmp <- rep(NA, ncol(nonCT_per_gene_CD4_datasets[[gene]]))
#   nonCT_per_gene_CD4_datasets[[gene]] <- rbind(nonCT_per_gene_CD4_datasets[[gene]], tmp)
#   rownames(nonCT_per_gene_CD4_datasets[[gene]])[3] <-
#     c("newborn","middle_age", "centenarian")[(!c("newborn","middle_age","centenarian") %in%
#                                                 rownames(nonCT_per_gene_CD4_datasets[[gene]]))]
#   # naming the new row
# }
# 
# for (gene in names(nonCT_per_gene_CD4_datasets)) {
#   nonCT_per_gene_CD4_datasets[[gene]] <- arrange(nonCT_per_gene_CD4_datasets[[gene]],
#                                               rownames(nonCT_per_gene_CD4_datasets[[gene]]))
#   # Put rows in the right order
# }
# 
# rm(p, i, k, tmp)

load("data_rmd/nonCT_per_gene_CD4_datasets.rda")
